Barneby Lives usage example

### 2023-05-15 scripts/project_template.Rmd
function to format for label type date

stringr::str_split(date, pattern = '/', simplify = T)[,2] # capture the month

date_text <- function(x, col2text){

  text_col <- !!enquo(col2text)

  month_tab <- data.frame(Month_Num = sprintf("%02d", 1:12), Month_Abb = month.abb)
  y <- format(as.Date(x[,col2text], format="%d/%m/%Y"), "%Y")
  d <- format(as.Date(x[,col2text], format="%d/%m/%Y"), "%d")
  m <- format(as.Date(x[,col2text], format="%d/%m/%Y"), "%m")
  m_text <- month_tab[m == month_tab$Month_Num, 'Month_Abb']

 # text <- paste0(d, ' ', m, ', ', y)
  return(m)

@@

t <- date_text(fourtet, 'date')

t %>% 
  mutate(dtest = date_text(., ))

t == month_tab$Month_Num
```

>>>>

#' take ISO 8601 date and make it written herbarium label format
#' 
#' @param x a data frame with dates
#' @param y the data frame holding Internationally formatted dates (day, month, year)
date2text <- function(x, col2text) {
  x$col2text <- as.Date(x[, col2text], format = "%d/%m/%Y")
  m <- as.numeric(format(x$col2text, "%m"))

  text <- paste0(format(x$col2text, "%d"), # just grab day of month here
                 ' ',
                 month.abb[m], # grab the abbrevation for the month here
                 ', ',
                 format(x$col2text, "%Y")) # grab the year here

  return(text)

@@

fourtet %>% 
  mutate(dtest = date2text(., 'date'))
